---
title: "Assignment"
description: |
  A short description of the post.
author:
  - name: Peirong LIN
    url: https://www.linkedin.com/in/perry-lin/
date: 07-13-2021
output:
  distill::distill_article:
    self_contained: false
---

# Mini Challenge case 2 

## 1. Environment Preparation

First, we set the fig.retina as 3 for higher resolution.

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.retina=3,
  echo = TRUE,
  eval = TRUE,
  message = FALSE, 
  warning = FALSE)
```

Here we import all the packages we need to use.

```{r,echo=TRUE,eval=TRUE}
packages <- c('raster','sf','tmap','clock','tidyverse','data.table','rgdal')
for (p in packages){
  if (!require(p,character.only = T)){
    install.packages(p)
  }
  library(p,character.only = T)
}
```

Then, we import the map given.

```{r}
bgmap <- raster("Geospatial/MC2-tourist.tif")
bgmap
```

```{r}
tmap_mode("plot")
tm_shape(bgmap) + 
  tm_raster(bgmap,
            legend.show = FALSE)
```

```{r}
tm_shape(bgmap) + 
tm_rgb(bgmap,r = 1, g = 2, b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255)
```

```{r}
Abila_st <- st_read(dsn = "Geospatial",
                    layer = "Abila")
```

## 2. Data preprocessing

First, import all the data we need.

```{r}
gps <- read_csv("gps.csv")
glimpse(gps)
```

```{r}
cc_data <- read_csv("cc_data.csv")
loyalty <- read_csv("loyalty_data.csv")
```

```{r}
car <- read_csv("car-assignments.csv")
```

Change timestamp to the correct format.

```{r}
gps$Timestamp <- date_time_parse(gps$Timestamp,
                                 zone = '',
                                 format = "%m/%d/%Y %H:%M:%S")
gps$day <- as.factor(get_day(gps$Timestamp))
gps$id <- as_factor(gps$id)
```

A brief overview to see the distribution of location in cc_data. 

```{r}
cc_data %>%
    group_by(location) %>%
    summarise(count=n()) %>%
    arrange(count)
```

Since some payment might not use loyalty card to record, the price will automatically goes to another column. Therefore, we need to put them back to the correct column. 

```{r}
loyalty$loyaltynum <- ifelse(is.na(loyalty$loyaltynum), loyalty$price, loyalty$loyaltynum)
```

```{r}
loyalty <- loyalty %>% mutate(price = ifelse(price %like% 'L', 0, price))
```

Change the price to correct format.

```{r}
loyalty$price <- as.numeric(loyalty$price)
```

Change timestamp in cc_data and loyalty data into correct format.

```{r}
cc_data$timestamp <- date_time_parse(cc_data$timestamp,
                                 zone = '',
                                 format = "%m/%d/%Y %H:%M")
cc_data$day <- as.factor(get_day(cc_data$timestamp))

loyalty$timestamp <- date_time_parse(loyalty$timestamp,
                                 zone = '',
                                 format = "%m/%d/%Y")
loyalty$day <- as.factor(get_day(loyalty$timestamp))
```

Combine cc_data and loyalty data together to answer question 1.

```{r}
comb <-merge(cc_data,loyalty, by=c("day","location","price"), all.x=TRUE, all.y=FALSE)
```


For better visualize in a chart, I add labels to each location instead of longer name of location.

```{r}
comb <- comb %>%
  mutate(Labels = case_when(
    location == "Abila Airport" ~ "1",
    location == "Abila Scrapyard" ~ "2",
    location == "Abila Zacharo" ~ "3",
    location == "Ahaggo Museum" ~ "4",
    location == "Albert's Fine Clothing" ~ "5",
    location == "Bean There Done That" ~ "6",
    location == "Brew've Been Served" ~ "7",
    location == "Brewed Awakenings" ~ "8",
    location == "Carlyle Chemical Inc." ~ "9",
    location == "Chostus Hotel" ~ "10",
    location == "Coffee Cameleon"~"11",
    location == "Coffee Shack"~"12",
    location == "Daily Dealz"~"13",
    location == "Desafio Golf Course"~"14",
    location == "Frank's Fuel"~"15",
    location == "Frydos Autosupply n' More"~"16",
    location == "Gelatogalore"~"17",
    location == "General Grocer"~"18",
    location == "Guy's Gyros"~"19",
    location == "Hallowed Grounds"~"20",
    location == "Hippokampos"~"21",
    location == "Jack's Magical Beans"~"22",
    location == "Kalami Kafenion"~"23",
    location == "Katerina's Cafe"~"24",
    location == "Kronos Mart"~"25",
    location == "Kronos Pipe and Irrigation"~"26",
    location == "Maximum Iron and Steel"~"27",
    location == "Nationwide Refinery"~"28",
    location == "Octavio's Office Supplies"~"29",
    location == "Ouzeri Elian"~"30",
    location == "Roberts and Sons"~"31",
    location == "Shoppers' Delight"~"32",
    location == "Stewart and Sons Fabrication"~"33",
    location == "U-Pump"~"34",
    ))
```

```{r}
comb %>%
    group_by(Labels) %>%
    summarise(count=n()) %>%
  ggplot(aes(x= Labels, y = count)) +
  geom_col()
```

Top 4 frequent place:

| Labels   | Location     | 
|:-----:|:------------- |
|   24   | Katerina's Cafe|
|   21   | Hippokampos|
|   19   | Guy's Gyros|
|   7   | Brew've Been Served|


## 3. Question answering

### Q1. Anomalies

First, we see how many payments that used loyalty cards (gourp by loyalty card) and its credit card.

```{r}
comb %>%
  group_by(loyaltynum) %>%
  count(last4ccnum)
```

From the above table, we can see that some loyalty cards had more than one credit card. Those abnormal loyalty cards L2070, L2247, L6119, L8566 and abnormal loyalty cards are 4795,7889,5368 and 8332.

```{r}
comb %>%
  group_by(loyaltynum) %>%
  count(last4ccnum) %>%
  filter(last4ccnum %in% c(4795,7889,5368,8332))
```


When I filter abnormal credit cards, I found that credit card 4795 usually used loyalty card L8566, which loyalty card L8566 is used together with 4795. Therefore, the correct link of loyalty card and credit card should be L2070 - 8332, L2247 - 5368, L6119 - 7889, L8566-4795. 

```{r}
#correction
comb[663,]$loyaltynum <- "L2070"
comb[662,]$loyaltynum <- "L8566"
comb[442,]$loyaltynum <- "L6119"
comb[445,]$loyaltynum <- "L2247"
```


### Q2. Adding car assignment data

Combine car assignment with gps

```{r}
gpscar <- merge(car,gps,by.x = c("CarID"), by.y = c("id"),all.x=FALSE,all.y =TRUE)
```

```{r eval=FALSE, include=FALSE}
gps1 <- gps %>%
  filter(Timestamp < "2014-01-06 23:59:00")
```

```{r}
gps_sf <- st_as_sf(gps,
                   coords = c("long","lat"),
                   crs = 4326)
```

```{r}
gps_path <- gps_sf %>%
  group_by(id,day) %>%
  summarize(m = mean(Timestamp),
            do_union = FALSE) %>%
  st_cast("LINESTRING")
```

```{r}
gps_path
```

```{r}
gps_path_selected <- gps_path %>%
  filter(id == 35)
tmap_mode("view")
tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
          alpha = NA,
          saturation = 0.5,
          interpolate = TRUE,
          max.value = 255) +
  tm_shape(gps_path_selected) +
  tm_lines()

```

After finishing checking all ids from 1 to 35, here is the record overview. ID 16 and 29 cannot find the correct plot.

| id   | Location     | 
|:-----:|:------------- |
|   1   | Albert's Fine Clothing,Brew've Been Served,Coffee Shack,Jack's Magical Beans,Hallowed Grounds|
|   2   | Albert's Fine Clothing,Bean There Done That,Brew've Been Served,General Grocer,Jack's Magical Beans,Kronos Mart|
|   3   | Albert's Fine Clothing,Bean There Done That,Brew've Been Served,Frank's Fuel,General Grocer,Jack's Magical Beans,Kronos Mart,Roberts and Sons|
|   4   | Albert's Fine Clothing,Bean There Done That,Brew've Been Served,Frank's Fuel,General Grocer,Jack's Magical Beans,Kronos Mart,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros|
|   5   | Albert's Fine Clothing,General Grocer,Jack's Magical Beans,Kronos Mart,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,U-Pump|
|   6   | Albert's Fine Clothing,Brew've Been Served,Coffee Cameleon,General Grocer,Jack's Magical Beans,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,U-Pump|
|   7   | Albert's Fine Clothing,Brew've Been Served,Carlyle Chemical Inc.,Chostus Hotel,General Grocer,Kronos Mart,Jack's Magical Beans,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,U-Pump|
|   8   | Albert's Fine Clothing,Brew've Been Served,Carlyle Chemical Inc.,General Grocer,Jack's Magical Beans,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,U-Pump|
|   9   | Albert's Fine Clothing,Brew've Been Served,Carlyle Chemical Inc.,General Grocer,Jack's Magical Beans,Hallowed Grounds,Guy's Gyros,U-Pump|
|   10   | Albert's Fine Clothing,Coffee Shack,General Grocer,Jack's Magical Beans,Guy's Gyros,U-Pump|
|   11   | Albert's Fine Clothing,Bean There Done That,Brew've Been Served,General Grocer,Jack's Magical Beans,General Grocer,Guy's Gyros,Hallowed Grounds,Roberts and Sons,U-Pump|
|   12   | Chostus Hotel,Kronos Mart,Roberts and Sons,General Grocer,Brew've Been Served,Frydos Autosupply n' More,Hallowed Grounds|
|   13   | Albert's Fine Clothing,Ahaggo Museum,Chostus Hotel,General Grocer,Roberts and Sons,Ouzeri Elian,Frydos Autosupply n' More,Brew've Been Served,Hallowed Grounds,Jack's Magical Beans,U-Pump|
|   14   | Albert's Fine Clothing, Bean There Done That,Brew've Been Served,Roberts and Sons,Jack's Magical Beans,Guy's Gyros,Carlyle Chemical Inc.,U-Pump,Kronos Mart,General Grocer,Ahaggo Museum|
|   15   | Ahaggo Museum,Jack's Magical Beans,Kronos Mart,Frank's Fuel,U-Pump,Guy's Gyros,Brew've Been Served,Abila Scrapyard,Hallowed Grounds,Frydos Autosupply n' More,Carlyle Chemical Inc.,Kronos Pipe and Irrigation|
|   16   | |
|   17   | Albert's Fine Clothing,Ahaggo Museum,Brew've Been Served,Chostus Hotel,U-Pump,Jack's Magical Beans,Roberts and Sons,General Grocer,Ouzeri Elian|
|   18   | Albert's Fine Clothing,Ahaggo Museum,Brew've Been Served,Chostus Hotel,Hallowed Grounds,Ouzeri Elian,|
|   19   | Albert's Fine Clothing,Brew've Been Served,Chostus Hotel,U-Pump,Jack's Magical Beans,Roberts and Sons,General Grocer,Ouzeri Elian|
|   20   | Albert's Fine Clothing,Frydos Autosupply n' More,Chostus Hotel,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Jack's Magical Beans,Coffee Cameleon|
|   21   | Albert's Fine Clothing,Ahaggo Museum,Chostus Hotel,Brew've Been Served,Carlyle Chemical Inc.,Roberts and Sons,General Grocer,Ouzeri Elian,Jack's Magical Beans,Coffee Cameleon|
|   22   | Albert's Fine Clothing,Ahaggo Museum,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Hallowed Grounds,Jack's Magical Beans|
|   23   | Albert's Fine Clothing,U-Pump,Hallowed Grounds,Kronos Mart,Roberts and Sons,General Grocer,Jack's Magical Beans|
|   24   | Albert's Fine Clothing,Ahaggo Museum,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Hallowed Grounds,Jack's Magical Beans,Brew've Been Served|
|   25   | Albert's Fine Clothing,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Hallowed Grounds,Jack's Magical Beans,Brew've Been Served,Coffee Cameleon,Guy's Gyros|
|   26   | Albert's Fine Clothing,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Hallowed Grounds,Jack's Magical Beans,Brew've Been Served,Guy's Gyros,Kronos Mart|
|   27   | Albert's Fine Clothing,U-Pump,Jack's Magical Beans,Hallowed Grounds,Roberts and Sons,General Grocer,Guy's Gyros|
|   28   | Kronos Pipe and Irrigation,Kronos Mart,Guy's Gyros|
|   29   | |
|   30   | Albert's Fine Clothing,U-Pump,Jack's Magical Beans,Chostus Hotel,Brew've Been Served,Roberts and Sons,Ahaggo Museum|
|   31   | Chostus Hotel,Brew've Been Served,Roberts and Sons,General Grocer,Hallowed Grounds|
|   32   | Albert's Fine Clothing,Brew've Been Served,U-Pump,Jack's Magical Beans,Hallowed Grounds,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Guy's Gyros|
|   33   | Albert's Fine Clothing,Ahaggo Museum,U-Pump,Jack's Magical Beans,Brew've Been Served,Roberts and Sons,General Grocer,Chostus Hotel,Guy's Gyros,Carlyle Chemical Inc.|
|   34   | Albert's Fine Clothing,Ahaggo Museum,U-Pump,Jack's Magical Beans,Brew've Been Served,Roberts and Sons,General Grocer,Chostus Hotel,Guy's Gyros|
|   35   | Albert's Fine Clothing,Ahaggo Museum,Chostus Hotel,Roberts and Sons,Brew've Been Served,General Grocer,U-Pump,Jack's Magical Beans|

Here we look at the location that each loyalty card owner would frequently go. 

```{r}
comb %>%
  filter(!is.na(loyaltynum)) %>%
  group_by(loyaltynum) %>%
  count(location)
```

From the above results, we can see that there are quite inconsistent between consuming data and vehicle data. I think the gps and car assignment data may need to modified. There are some payments place cannot be found in the map.

### Q3. Owners of credit cards

Comparing the result of loyalty card data and car assignment data, I think the relationship between ids and loyalty card is as following:

|last name |First name | id   | loyalty card   | 
|:-----:|:-----:|:-----:|:------------- |
|   Cazar   | Gustav| 9 | L2070 |
|   Dedos   | Lidelse| 14 | L2490 |
|   Bodrogi   | Loreto| 15 | L1485 |
|   Frente   | Vira| 19 | L8328 |
|   Borrasca   | Isande| 28 | L1107 |


### Q4. Potential Relationship 

Here are all the ids who visited to GAStech.

| id   | Location     | 
|:-----:|:------------- |
|   1   | Albert's Fine Clothing,Brew've Been Served,Coffee Shack,Jack's Magical Beans,Hallowed Grounds,GAStech|
|   2   | Albert's Fine Clothing,Bean There Done That,Brew've Been Served,General Grocer,Jack's Magical Beans,Kronos Mart,GAStech|
|   3   | Albert's Fine Clothing,Bean There Done That,Brew've Been Served,Frank's Fuel,General Grocer,Jack's Magical Beans,Kronos Mart,Roberts and Sons,GAStech|
|   4   | Albert's Fine Clothing,Bean There Done That,Brew've Been Served,Frank's Fuel,General Grocer,Jack's Magical Beans,Kronos Mart,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,GAStech|
|   5   | Albert's Fine Clothing,General Grocer,Jack's Magical Beans,Kronos Mart,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,GAStech|
|   6   | Albert's Fine Clothing,Brew've Been Served,Coffee Cameleon,General Grocer,Jack's Magical Beans,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,U-Pump,GAStech|
|   7   | Albert's Fine Clothing,Brew've Been Served,Carlyle Chemical Inc.,Chostus Hotel,General Grocer,Kronos Mart,Jack's Magical Beans,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,U-Pump,GAStech|
|   8   | Albert's Fine Clothing,Brew've Been Served,Carlyle Chemical Inc.,General Grocer,Kronos Mart,Jack's Magical Beans,Roberts and Sons,Hallowed Grounds,Ouzeri Elian,Guy's Gyros,U-Pump,GAStech|
|   9   | Albert's Fine Clothing,Brew've Been Served,Carlyle Chemical Inc.,General Grocer,Jack's Magical Beans,Hallowed Grounds,Guy's Gyros,U-Pump,GAStech|
|   10   | Albert's Fine Clothing,Coffee Shack,General Grocer,Jack's Magical Beans,Guy's Gyros,U-Pump,GAStech|
|   11   | Albert's Fine Clothing,Bean There Done That,Brew've Been Served,General Grocer,Jack's Magical Beans,General Grocer,Guy's Gyros,Hallowed Grounds,Roberts and Sons,U-Pump,GAStech|
|   12   | Chostus Hotel,Kronos Mart,Roberts and Sons,General Grocer,Brew've Been Served,Frydos Autosupply n' More,Hallowed Grounds,GAStech|
|   13   | Albert's Fine Clothing,Ahaggo Museum,Chostus Hotel,General Grocer,Roberts and Sons,Ouzeri Elian,Frydos Autosupply n' More,Brew've Been Served,Hallowed Grounds,Jack's Magical Beans,U-Pump,GAStech|
|   14   | Albert's Fine Clothing, Bean There Done That,Brew've Been Served,Roberts and Sons,Jack's Magical Beans,Guy's Gyros,Carlyle Chemical Inc.,U-Pump,Kronos Mart,General Grocer,Ahaggo Museum,GAStech|
|   15   | Ahaggo Museum,Jack's Magical Beans,Kronos Mart,Frank's Fuel,U-Pump,Guy's Gyros,Brew've Been Served,Abila Scrapyard,Hallowed Grounds,Frydos Autosupply n' More,Carlyle Chemical Inc.,Kronos Pipe and Irrigation,GAStech|
|   17   | Albert's Fine Clothing,Ahaggo Museum,Brew've Been Served,Chostus Hotel,U-Pump,Jack's Magical Beans,Roberts and Sons,General Grocer,Ouzeri Elian,GAStech|
|   18   | Albert's Fine Clothing,Ahaggo Museum,Brew've Been Served,Chostus Hotel,Hallowed Grounds,Ouzeri Elian,GAStech|
|   19   | Albert's Fine Clothing,Brew've Been Served,Chostus Hotel,U-Pump,Jack's Magical Beans,Roberts and Sons,General Grocer,Ouzeri Elian,GAStech|
|   20   | Albert's Fine Clothing,Frydos Autosupply n' More,Chostus Hotel,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Jack's Magical Beans,Coffee Cameleon,GAStech|
|   21   | Albert's Fine Clothing,Ahaggo Museum,Chostus Hotel,Brew've Been Served,Carlyle Chemical Inc.,Roberts and Sons,General Grocer,Ouzeri Elian,Jack's Magical Beans,Coffee Cameleon,GAStech|
|   22   | Albert's Fine Clothing,Ahaggo Museum,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Hallowed Grounds,Jack's Magical Beans,GAStech|
|   23   | Albert's Fine Clothing,U-Pump,Hallowed Grounds,Kronos Mart,Roberts and Sons,General Grocer,Jack's Magical Beans,GAStech|
|   24   | Albert's Fine Clothing,Ahaggo Museum,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Hallowed Grounds,Jack's Magical Beans,Brew've Been Served,GAStech|
|   25   | Albert's Fine Clothing,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Hallowed Grounds,Jack's Magical Beans,Brew've Been Served,Coffee Cameleon,Guy's Gyros,GAStech|
|   26   | Albert's Fine Clothing,U-Pump,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Hallowed Grounds,Jack's Magical Beans,Brew've Been Served,Guy's Gyros,Kronos Mart,GAStech|
|   27   | Albert's Fine Clothing,U-Pump,Jack's Magical Beans,Hallowed Grounds,Roberts and Sons,General Grocer,Guy's Gyros,GAStech|
|   28   | Kronos Pipe and Irrigation,Kronos Mart,Guy's Gyros,GAStech|
|   30   | Albert's Fine Clothing,U-Pump,Jack's Magical Beans,Chostus Hotel,Brew've Been Served,Roberts and Sons,Ahaggo Museum,GAStech|
|   31   | Chostus Hotel,Brew've Been Served,Roberts and Sons,General Grocer,Hallowed Grounds,GAStech|
|   32   | Albert's Fine Clothing,Brew've Been Served,U-Pump,Jack's Magical Beans,Hallowed Grounds,Kronos Mart,Roberts and Sons,General Grocer,Ouzeri Elian,Guy's Gyros,GAStech|
|   33   | Albert's Fine Clothing,Ahaggo Museum,U-Pump,Jack's Magical Beans,Brew've Been Served,Roberts and Sons,General Grocer,Chostus Hotel,Guy's Gyros,Carlyle Chemical Inc.,GAStech|
|   34   | Albert's Fine Clothing,Ahaggo Museum,U-Pump,Jack's Magical Beans,Brew've Been Served,Roberts and Sons,General Grocer,Chostus Hotel,Guy's Gyros,GAStech|
|   35   | Albert's Fine Clothing,Ahaggo Museum,Chostus Hotel,Roberts and Sons,Brew've Been Served,General Grocer,U-Pump,Jack's Magical Beans,GAStech|

Since almost every id goes to GAStech, I think all of them are the staff of GAStech. However, ID 12 comes from hotel, which means he/she might not be the resident in this area. 

### Q5. Suspicious Activity

From the above analysis, there are some places that are suspicious:
1. Frank's Fuel with ID 9 or 15.

2. Kronos Capitol with rarely people visited.

3. Parla Park with rarely people visited.





